Title Goes Here

### 2020-02-25 paper/paper.tex
More forward references to rewrite rules in flowchart

    \node (marksubs1) [process, below of=handleprim]{($C$) Mark sub-expressions};
    \node (marksubs2) [process, below of=handleapp]{($C$) Mark sub-expressions};

    \node (onebranch) [process, below of=handlecase]{($B$) Transform one branch};
    \node (prodmatch) [process, below of=onebranch]{($P$) Transform one field in product match of current branch};
    \node (abstractvar) [process, below of=prodmatch]{($P$) Abstract the pattern variable of the field with \ttt{Lam} and \ttt{Var}};
    \node (markbody) [process, below of=abstractvar]{($P$) Mark branch body};
    \node (endstep) [process, below of=markbody, right of=markbody, xshift=1.6cm]{End of one transformation step};

>>>>

    \node (marksubs1) [process, below of=handleprim]{($C, M$) Mark sub-expressions};
    \node (marksubs2) [process, below of=handleapp]{($C, M$) Mark sub-expressions};

    \node (onebranch) [process, below of=handlecase]{($B$) Transform one branch};
    \node (prodmatch) [process, below of=onebranch]{($P$) Transform one field in product match of current branch};
    \node (abstractvar) [process, below of=prodmatch]{($P, A$) Abstract the pattern variable of the field with \ttt{Lam} and \ttt{Var}};
    \node (markbody) [process, below of=abstractvar]{($P, M$) Mark branch body};
    \node (endstep) [process, below of=markbody, right of=markbody, xshift=1.6cm]{End of one transformation step};
